ZCB Pricing

### 2018-08-02 ZCB Pricing .Rmd
small change

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(n)
  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments

>>>>

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r
  z=rnorm(n)
  z_m= z-mean(z) # Moment matching transformation of RV to match finite moments
